---
title: "CaseStudy02_GDA"
output: html_notebook
---

Case Study 2: How Can a Wellness Technology
Company Play It Smart?

```{r}
library(tidyverse)
library(lubridate)
library(dplyr)
library(ggplot2)
library(tidyr)
```

Using Daily activity, calories, intensities and steps

```{r}
act <- read_csv("C:/Users/Hafiz Asyraaf/OneDrive/Desktop/UMP DOC/Google Data Analytics Cert/Dataset Capstone/bellabeat/dailyActivity_merged.csv")
cal<- read_csv("C:/Users/Hafiz Asyraaf/OneDrive/Desktop/UMP DOC/Google Data Analytics Cert/Dataset Capstone/bellabeat/dailyCalories_merged.csv")
int<- read_csv("C:/Users/Hafiz Asyraaf/OneDrive/Desktop/UMP DOC/Google Data Analytics Cert/Dataset Capstone/bellabeat/dailyIntensities_merged.csv")
step<- read_csv("C:/Users/Hafiz Asyraaf/OneDrive/Desktop/UMP DOC/Google Data Analytics Cert/Dataset Capstone/bellabeat/dailySteps_merged.csv")
view(int)
view(act)
view(cal)
view(step)

```
Exploring dataset


```{r}
n_distinct(act$Id)
n_distinct(cal$Id)
n_distinct(int$Id)
n_distinct(step$Id)

```

This information tells us about number participants in each data sets. So, based on the output, the duplicated dataset shows 33 for all data.

```{r}
# activity

summary(act)

summary(cal)

summary(int)

summary(step)

```
Vizualize
```{r}
ggplot(data=merged_data, aes(x=TotalMinutesAsleep, y=SedentaryMinutes)) + 
geom_point(color='darkblue') + geom_smooth() +
  labs(title="Minutes Asleep vs. Sedentary Minutes")

```
Correlation between total steps and calories. The more steps, the more calories burned.

```{r}
library(ggplot2)

ggplot(data = act, aes(x = TotalSteps)) +
  geom_line(aes(y = SedentaryMinutes, LightlyActiveMinutes, FairlyActiveMinutes, VeryActiveMinutes, color = "Y1")) +
  geom_line(aes(y = LightlyActiveMinutes, color = "Y2")) +
  geom_line(aes(y = FairlyActiveMinutes, color = "Y3")) +
  geom_line(aes(y = VeryActiveMinutes, color = "Y4"))
  labs(title = "Line Plot with Multiple Y-axes", x = "X Axis Label") +
  scale_color_manual(values = c("Y1" = "blue", "Y2" = "red", "Y3" = "green", "")) +
  theme_minimal()

```

```{r}

library(ggplot2)

# Assuming 'cal' is your data frame
# Replace 'ActivityDay' and 'Calories' with your actual column names

# Create the bar plot
p <- ggplot(data = cal, aes(x = ActivityDay, y = Calories)) +
  geom_bar(stat = "identity", fill = "blue", alpha = 0.7) +
  labs(title = "Bar Plot of Calories by Activity Day", x = "Activity Day", y = "Calories") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Find the day with the highest and lowest calories
highest_calories <- cal$ActivityDay[which.max(cal$Calories)]
lowest_calories <- cal$ActivityDay[which.min(cal$Calories)]

# Add labels for highest and lowest values
p +
  geom_text(aes(label = "Highest", y = max(cal$Calories) + 50), 
            data = data.frame(ActivityDay = highest_calories), 
            vjust = -0.5, color = "darkgreen", size = 4) +
  geom_text(aes(label = "Minimum", y = min(cal$Calories) - 50), 
            data = data.frame(ActivityDay = lowest_calories), 
            vjust = 1.5, color = "red", size = 4)

```

